---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r, echo=TRUE}
d<-read.csv("activity.csv", sep=",")
d$date<-as.Date(d$date, "%Y-%m-%d")
install.packages('ggplot2', repos='https://cran.uni-muenster.de/')
library(ggplot2)
```



## What is mean total number of steps taken per day?
### Calculation the total number of steps taken per day
```{r, echo=TRUE}
dg<-aggregate(steps~date, d, sum)

```
### Histogram of the total number of steps taken each day
```{r, echo=TRUE}
hist(dg$steps)
```
### Calculattion and reporting the mean and median of the total number of steps taken per day
```{r, echo=TRUE}
summary(dg$steps)
```

## What is the average daily activity pattern?
### Time series plot of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r, echo=TRUE}
i<-na.omit(d)
i<-aggregate(steps~interval, i, mean)
with(i, plot(interval, steps, type="l"))
```
### 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps
```{r, echo=TRUE}
max<-which(i$steps==max(i$steps))
i$interval[max]
```

## Imputing missing values
### Calculating and reporting the total number of missing values in the dataset
```{r, echo=TRUE}
sum(is.na(d$steps))
```
### A strategy for filling in all of the missing values in the dataset. Creating a new dataset that is equal to the original dataset but with the missing data filled in
```{r, echo=TRUE}
nas<-which(is.na(d$steps))
d1<-d
for (k in nas) {
	na_int<-d$interval[k]
	n<-subset(d, interval==na_int)
	d1$steps[k]<-mean(na.omit(n$steps))
}
```
### Histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day
```{r, echo=TRUE}
d1g<-aggregate(steps~date, d1, sum)
hist(d1g$steps)
summary(d1g$steps)
```
The median in second case a bit higher (10770 vs 10760)

## Are there differences in activity patterns between weekdays and weekends?
### A new factor variable in the dataset with two levels – “weekday” and “weekend”
```{r, echo=TRUE}
d1$day<-weekdays(d1$date)
for (m in 1:nrow(d1)){
if (d1$day[m]=="âîñêðåñåíüå"|d1$day[m]=="ñóááîòà") 
	{d1$weektime[m]<-"weekend"
	} 
	else 
	{d1$weektime[m]<-"weekday"
	}
}
```
### A panel plot containing a time series plot
```{r, echo=TRUE}
d2g<-aggregate(steps~weektime+interval, d1,mean)
d2g$weektime<-as.factor(d2g$weektime)
qplot(interval, steps, data=d2g, facets=weektime~., geom='line')
```

